Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-17 paper.qmd
Updated Figure 2 title
Updated the distances between clusters

```{r}
#| label: hexbin-two-curvy
## Compute hexbin parameters
num_bins_x_two_curvy <- 10

@@

```{r}
#| label: fig-two-curvy-true-proj
#| fig-cap: "Two views of the true model (blue lines) in $2\\text{-}D$ projections from $7\\text{-}D$, for the two C-shaped clusters data (grey points). The data is spread along the non-linear shaped clusters, and does not vary much from the curves. The **langevitour** software is used to view the data with a tour, and the full video is available at <>." 
#| fig-pos: H
#| fig-width: 10
#| fig-height: 5

>>>>

```{r}
#| label: hexbin-two-curvy
## Compute hexbin parameters
num_bins_x_two_curvy <- 15

@@

```{r}
#| label: fig-two-curvy-true-proj
#| fig-cap: "Two views of the true model (blue lines) in $2\\text{-}D$ projections from $7\\text{-}D$, for the two C-shaped clusters data (grey points). In one C-shaped cluster, the data is spread throughout the cluster, while in the other C-shaped cluster, the data is concentrated more in one corner of the cluster. The **langevitour** software is used to view the data with a tour, and the full video is available at <>." 
#| fig-pos: H
#| fig-width: 10
#| fig-height: 5
